---
title: "DateTime-Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DateTime-Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
This is a user guide for the `DateTime` package, which allows you to perform operations or calculations with date and time. See this guide for explanations and examples of the functions in this package. 

### Installation
To use the `DateTime` package, use the code below in your console. 

```{r setup, eval=TRUE, echo=TRUE}
# Use package devtools 
install.packages("DateTime")

# Load the DateTime package in 
library(DateTime)
```

### Fuctions of the package 
The package contains 4 functions which are related to date and time. 

- `date_difference()`

- `add_time()`

- `is_same_day()`

- `is_dutch_holiday()`


#### Calculating date difference 
The `date_difference()` function allows you to calculate the difference between two dates. The function uses various time units such as seconds, minutes, hours, days, weeks, months, and years.

```{r, date_difference, echo=TRUE, eval=TRUE}
# Load the DateTime package
library(DateTime)

# Calculate the difference between two dates in days
time_difference("2024-05-21", "2024-05-22", units = "days")

# Calculate the difference between two dates in weeks
time_difference("2024-05-21", "2024-06-21", units = "weeks")

# Calculate the difference between two dates in years
time_difference("2024-05-21", "2025-05-21", units = "years")

```

